
---
title: "Lab 1: Airbnbs in NYC"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
library(palmerpenguins)
```

## Airbnb in NYC (or your city)

Airbnb is a startup company that has had a disruptive effect on the hotel, rental home, and 
vacation industry throughout the world. The success of Airbnb has not come without controversies, with critics arguing that it Airbnb has negative impacts on housing and rental
prices and also on the daily lives of people living in neighborhoods where Airbnb is popular.
This controversy has been particularly intense in NYC, where the debate been Airbnb proponents
and detractors eventually led to the city imposing strong regulations on the use of Airbnb.

Because Airbnb listings are available online through their website and app, it is possible
for us to acquire and visualize the impacts of Airbnb on different cities, including 
New York City. This is possible through the work of an organization called 
[inside airbnb](https://insideairbnb.com/get-the-data/)

## First Steps

Before we introduce the data and the main assignment, let's begin with a few key 
steps to configure the file and create a github repository for your first assignment.

-   Update the YAML, changing the author name to your name, and **knit** the document.
-   Commit your changes with a meaningful commit message.
-   Push your changes to GitHub.
-   Go to your repo on GitHub and confirm that your changes are visible in your Qmd **and** md files. If anything is missing, commit and push again.



```{r}
#| label: plot-penguins
#| warning: false
#| echo: false

ggplot(penguins, 
       aes(x = flipper_length_mm, y = bill_length_mm)) +
  geom_point(aes(color = species, shape = species)) +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(
    title = "Flipper and bill length",
    subtitle = "Dimensions for penguins at Palmer Station LTER",
    x = "Flipper length (mm)", y = "Bill length (mm)",
    color = "Penguin species", shape = "Penguin species"
  ) +
  theme_minimal()
```
